Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-06-19 edubots_surveys.Rnw
Adding Declarations section

\author[
  addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
  corref={aff1},                       % id of corresponding address, if any
  email={jmerelo@ugr.es}   % email address
]{\inits{J.J.}\fnm{Juan J.} \snm{Merelo}}
\author[
  addressref={aff1},
  email={pacv@ugr.es}   % email address
]{\inits{P.A.}\fnm{Pedro A.} \snm{Castillo}}
\author[
  addressref={aff2},
  email={amorag@ugr.es}
]{\inits{A.M.G}\fnm{Antonio M.} \snm{Mora}}
\author[
  addressref={aff1},
  email={fbarranco@ugr.es}
]{\inits{F.}\fnm{Francisco} \snm{Barranco}}
\author[
  addressref={aff3},
  email={n.h.abbas@leeds.ac.uk}
]{\inits{N.}\fnm{Noorhan} \snm{Abbas}}

@@

@@

@@

\section{Conclusions}

@@

\section*{Acknowledgements}%% if any

@@

>>>>

\author[
  addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
  corref={aff1},                       % id of corresponding address, if any
  email={jmerelo@ugr.es}   % email address
]{\inits{J.J.M.}\fnm{Juan J.} \snm{Merelo}}
\author[
  addressref={aff1},
  email={pacv@ugr.es}   % email address
]{\inits{P.A.C.}\fnm{Pedro A.} \snm{Castillo}}
\author[
  addressref={aff2},
  email={amorag@ugr.es}
]{\inits{A.M.M}\fnm{Antonio M.} \snm{Mora}}
\author[
  addressref={aff1},
  email={fbarranco@ugr.es}
]{\inits{F.B.}\fnm{Francisco} \snm{Barranco}}
\author[
  addressref={aff3},
  email={n.h.abbas@leeds.ac.uk}
]{\inits{N.A.}\fnm{Noorhan} \snm{Abbas}}

% Antonio - Olia and Alberto are missing. ;)

@@

% ********************** INTRODUCTION ****************************

@@

% ********************** METHODOLOGY ****************************

@@

\section{Conclusions}
\label{sec:concl}

@@

% ********************** DECLARATIONS ****************************

\section{Declarations}
\label{sec:decl}

\subsection{Availability of data and materials}

The datasets generated and analysed during the current study are available in the [NAME] repository, accesible from [PERSISTENT WEB LINK TO DATASETS]

\subsection{Competing interests}

The authors declare that they have no competing interests.

% Antonio - If there is any, please indicate.

\subsection{Funding}

@@

\subsection{Authors' contributions}

All the authors have contributed to the study presented in this manuscript. 
JJM has been the leader...
PAC has...
AMM has ...
FB has...
NA has...
OT has...
AG has...
All authors read and approved the final manuscript.

% Antonio - here we can explain what we have done author briefly.

\subsection{Acknowledgements}

The authors want to thank to the educators who participated in the survey.
% Antonio - Add other acknowledgements
